Toronto's COVID-19 Impact: Effect of Age and Gender on Outcomes

### 2024-09-24 paper/paper.qmd
changes to paper and readme

---
title: "Toronto's COVID-19 Impact: Effect of Age and Gender on Outcomes"
author: 
  - Dhruv Gupta
thanks: "Code and data are available at: https://github.com/dhruv5423/Covid19-R-Project"
date: "today"
date-format: long
abstract: "The COVID-19 Pandemic caused irreparable damage to the infrastructure of our global systems, highlighting the neccessity to better understand factors that influence health outcomes. This paper uses data from OpenDataToronto to investigate how age and gender affects outcomes of those infected with the virus. We find that in Toronto, age is strongly correlated with mortality and poorer hospitalisation outcomes. Further, we find that males in Toronto are almost 1.4 times more likely to die from COVID-19 than females."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
header-includes:
  - \usepackage{float}
---

>>>>

---
title: "Toronto's COVID-19 Impact: Effect of Age and Gender on Outcomes"
author: 
  - Dhruv Gupta
thanks: "Code and data are available at: https://github.com/dhruv5423/Covid19-R-Project"
date: "today"
date-format: long
abstract: "The COVID-19 Pandemic caused irreparable damage to the infrastructure of our global systems, highlighting the neccessity to better understand factors that influence health outcomes. This paper uses data from OpenDataToronto to investigate how age and gender affects outcomes of those infected with the virus. We find that in Toronto, age is strongly correlated with mortality and poorer hospitalisation outcomes. Further, we find that males have significantly worse outcomes than females in both mortality rates and hopsitalisation outcomes"
format: pdf
toc: true
number-sections: true
bibliography: references.bib
header-includes:
  - \usepackage{float}
---
